### 2023-03-30 resilience.tex
Theorem -> Thm in the tableau

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\uparrow$~ & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~ & $\downarrow$~ $\downarrow$~ \\ \hline
   RP & Decidable (Theorem~\ref{up-up}) & Decidable (Theorem~\ref{down-up})  & Decidable (Theorem~\ref{up-down}) & Undecidable (Theorem~\ref{down-down}) \\ \hline
   BRP & Decidable (Corollary~\ref{B-up-up}) &  Decidable (Theorem~\ref{down-up}) & ?? & ?? \\ \hline
      kRP & Decidable (Theorem~\ref{k-up-up}) & Decidable (Theorem~\ref{down-up}) & ?? & ?? \\ \hline
 \end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad & $\uparrow$~ $\uparrow$~ & $\uparrow$~ $\downarrow$~ & $\downarrow$~ $\uparrow$~ & $\downarrow$~ $\downarrow$~ \\ \hline
   RP & Decidable (Thm~\ref{up-up}) & Decidable (Thm~\ref{down-up})  & Decidable (Thm~\ref{up-down}) & Undecidable (Thm~\ref{down-down}) \\ \hline
   BRP & Decidable (Corollary~\ref{B-up-up}) &  Decidable (Thm~\ref{down-up}) & ?? & ?? \\ \hline
      kRP & Decidable (Thm~\ref{k-up-up}) & Decidable (Thm~\ref{down-up}) & ?? & ?? \\ \hline
 \end{tabular}
\end{center}
